---
title: "Cohort Analysis"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(warning = F,
                      message = F,
                      echo = F)

library(ggplot2)
library(reader)
library(ggthemes)
library(knitr)
library(rmarkdown)
library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)
library(shiny)
library(shinydashboard)
library(dashboardthemes)
library(shinyWidgets)
library(forcats)
library(readr)
library(readxl)
library(tibble)
library(kableExtra)
library(gt)

```

## Info About Files

Notes:
* Go through each of the original sales files, get all the column names for each file, recycle the file name and add to column names for each

Additional Context:


```{r}

file_list <- list.files("Data")

file_data <- tibble()

for(i in file_list){
  
  curr_file <- read_csv(file = paste0("Data\\", i))
  
  curr_file_data <- tibble(
    file_nm = i,
    col_nms = colnames(curr_file)
  )
  
  file_data <- bind_rows(file_data, curr_file_data)
  
}

```

## Gather Transaction Data

Notes:
* Append all sources together with just the relevant columns - date of event, cancellation (if applicable), product, order totals, product price
* Creates a new column that is the customer email lowercase as casing varies by order for some customers. And if the casing is different, then the emails will appear to be different. 

Additional Context:
* Very few cancellation dates
* For Boldv1 - assuming that inactive_date is the same as cancellation date
* Boldv2 doesn't have the product name
* cancelled_at is not populated for any rows in GiveOrders or Shopify

```{r}

big_comm <- read_csv(file = "Data\\2021-01-07-bc-orders.csv") %>% 
  rename_all(~ tolower(x = .)) %>%
  rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>% 
  rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>% 
  rename_all(~ gsub(pattern = "(", replacement = "", x = ., fixed = T)) %>% 
  rename_all(~ gsub(pattern = ")", replacement = "", x = ., fixed = T)) %>% 
  mutate(order_date = dmy(order_date),
         order_id = as.character(order_id)) %>% 
  select(order_id, customer_email, order_date, order_total_inc_tax, product_details) %>% 
  rename(order_total = "order_total_inc_tax") %>% 
  mutate(file_source = "BigcommerceOrders.csv") %>% 
  rowwise() %>% 
  mutate(product_price = as.double(str_remove_all(string = str_split(string = str_split(string = product_details, 
                                                                                        pattern = ",")[[1]][length(str_split(string = product_details, 
                                                                                                                             pattern = ",")[[1]])], 
                                                                     pattern = ":", n = 2)[[1]][2], 
                                                  pattern = "[:space:]"))) %>% 
  ungroup() %>% 
  mutate(product_price = case_when(
    str_detect(string = product_details, pattern = "Product ID: 3805|Product ID: 5100|Product ID: 4295|Product ID: 3798|Product ID: 3805") ~ 10,
    str_detect(string = product_details, pattern = "Product ID: 3797") ~ 5,
    str_detect(string = product_details, pattern = "Product ID: 3799") ~ 15,
    str_detect(string = product_details, pattern = "Product ID: 3966") ~ 50,
    str_detect(string = product_details, pattern = "Product ID: 3800|Product ID: 5104") ~ 25,
    TRUE ~ product_price))

# Commented out but leaving in just in case Bold ever comes up again

# bold_v1 <- read_csv(file = "Data\\Boldv1.csv") %>% 
#   rename_all(~ tolower(x = .)) %>%
#   rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>% 
#   rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>% 
#   select(subscription_id, customer_e_mail, 
#          inactive_date,  
#          subscription_date, products, total_value_of_all_products_shipped) %>% 
#   mutate(subscription_date = mdy(subscription_date),
#          inactive_date = mdy(inactive_date)) %>% 
#   rename(order_date = "subscription_date",
#          customer_email = "customer_e_mail",
#          order_total = "total_value_of_all_products_shipped",
#          product_details = "products",
#          canceled_date = "inactive_date",
#          order_id = "subscription_id") %>% 
#   mutate(order_id = as.character(order_id),
#          file_source = "Boldv1.csv") %>% 
#   rowwise() %>% 
#   mutate(product_price = 
#            as.double(str_remove_all(string = str_split(string = 
#                                                          str_split(string = product_details, pattern = "-")[[1]][length(str_split(string = product_details,
#                                                                                                                                   pattern = "-")[[1]])], 
#                                                        pattern = "x")[[1]][1], pattern = "[:space:]"))) %>% 
#   ungroup()

# bold_v2 <- read_csv(file = "Data\\Boldv2.csv") %>%   # Maybe skip this for now since it's missing the product??
# # tt <- bold_v2 %>%
#   rename_all(~ tolower(x = .)) %>%
#   rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>%
#   rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>%
#   rename_all(~ gsub(pattern = "/", replacement = "_", x = ., fixed = T)) %>%
#   mutate(products = "None in file") %>% 
#   select(subscription_id, customer_email, created_at,
#          canceled_at,  # Maybe need - think about it
#          products,  # Not finding this
#          total_value_charged) %>% 
#   mutate(created_at = ymd_hms(created_at),
#          created_at = date(created_at),
#          canceled_at = ymd_hms(canceled_at),
#          canceled_at = date(canceled_at)) %>% 
#   rename(order_date = "created_at",
#          customer_email = "customer_email",
#          order_total = "total_value_charged",
#          product_details = "products",
#          canceled_date = "canceled_at",
#          order_id = "subscription_id") %>%
#   mutate(order_id = as.character(order_id),
#          file_source = "Boldv2.csv") %>% 
#   mutate(product_price = 10)

give_orders <- read_csv(file = "Data\\2022-01-07_Give.csv") %>% 
  rename_all(~ tolower(x = .)) %>%
  rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>% 
  rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>% 
  select(id, email, created_at, lineitem_name, total, lineitem_price) %>% 
  mutate(created_at = ymd(str_sub(string = created_at, start = 1, end = 10)),
         id = format(id, scientific = F)) %>% 
  rename(customer_email = "email",
         order_date = "created_at",
         product_details = "lineitem_name",
         order_total = "total",
         order_id = "id",
         product_price = "lineitem_price") %>% 
  mutate(order_id = as.character(order_id),
         file_source = "GiveOrders.csv") %>% 
  filter(!is.na(product_price))  

# Leaving in if MiniBC ever comes up again

# mini_bc <- read_csv(file = "Data\\MiniBC.csv") %>% 
#   rename_all(~ tolower(x = .)) %>%
#   rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>% 
#   rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>% 
#   rename_all(~ gsub(pattern = "/", replacement = "_", x = ., fixed = T)) %>% 
#   select(email_address, signup_date, product_name, charge_total, product_price) %>% 
#   mutate(signup_date = date(mdy_hm(signup_date))) %>% 
#   rename(customer_email = "email_address",
#          order_date = "signup_date",
#          order_total = "charge_total",
#          product_details = "product_name") %>% 
#   add_rownames(var = "order_id") %>%  # No ID found in this source, making one up from row number
#   mutate(order_id = as.character(order_id),
#          file_source = "MiniBC.csv")

shopify <- read_csv(file = "Data\\2022-01-07_Shopify.csv") %>% 
  rename_all(~ tolower(x = .)) %>%
  rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>% 
  rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>% 
  select(id, email, created_at, lineitem_name, total, lineitem_price) %>% 
  mutate(created_at = date(with_tz(time = ymd_hms(created_at), tzone = "America/Chicago")),
         id = format(id, scientific = F)) %>% 
  rename(customer_email = "email",
         order_date = "created_at",
         order_total = "total",
         product_details = "lineitem_name",
         order_id = "id",
         product_price = "lineitem_price") %>% 
  mutate(order_id = as.character(order_id),
         file_source = "ShopifyOrders.csv")

platform_data <- bind_rows(big_comm, 
                           # bold_v1, bold_v2, 
                           give_orders, 
                           # mini_bc, 
                           shopify) %>% 
  mutate(customer_email_lower = str_to_lower(string = customer_email)) %>%   # Unique customers based on this
  mutate(yr_mo_order = ymd(paste(year(order_date), month(order_date), "1", sep = "-")))

```

## Classify Product Cohorts

Notes:
* Each row was classified according to the cohort it would fall under. Later, just the first order for each customer was used to assign all orders to the cohort of the first purchase. 
* Classifying clients based on their first known purchase. Classifying them by year and month of that purchase as well as if they were an alternate entry or bonus entry lead or if they were not in these lead lists, by the product they purchased classified as either Member or One-time. Product classifications and leads were provided by Neil. 
* Further classified customers into sub groups (where applicable). For example, One-Time purchases classified further as either 5, 10 dollars,  etc

Additional Context:
* Rounding for sub-group classification applied where appropriate. For example, 24.99 and 25 were both considered 25.

```{r}

alt_entry_customers <- read_csv(file = "Data\\AlternateEntryCustomers.csv") %>% 
  rename_all(~ tolower(x = .)) %>%
  rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>% 
  rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>% 
  select(email, klaviyo_id, profile_created_on) %>% 
  mutate(email = str_to_lower(string = email))

bonus_entry_leads <- read_csv(file = "Data\\BonusEntryCustomers.csv") %>% 
  rename_all(~ tolower(x = .)) %>%
  rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>% 
  rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>% 
  select(email, profile_created_on, total_customer_lifetime_value) %>% 
  mutate(email = str_to_lower(string = email))

products_classified <- read_csv(file = "Data\\ProductsClassified.csv") %>% 
  rename_all(~ tolower(x = .)) %>%
  rename_all(~ gsub(pattern = " ", replacement = "_", x = .)) %>% 
  rename_all(~ gsub(pattern = "-", replacement = "_", x = .)) %>% 
  mutate(grp = case_when(
    str_detect(string = classification, pattern = "Member") ~ "Member",
    str_detect(string = classification, pattern = "bonus") ~ "Bonus",
    str_detect(string = classification, pattern = "One-time") ~ "One-time",
    TRUE ~ "Other")) %>% 
  mutate(grp = case_when(
    str_detect(string = product_details, pattern = "Product ID: 3805|Product ID: 5100|Product ID: 4295|Product ID: 3798|Product ID: 3797|Product ID: 3799|Product ID: 3966|Product ID: 3800|Product ID: 5104") ~ "Member",
    TRUE ~ grp
  ))

platform_data_classified <- platform_data %>% 
  filter(!(product_details %in% c(products_classified$product_details[products_classified$grp == "Bonus"]))) %>%  # Excluding bonus products
  filter(!(str_detect(string = product_details, pattern = fixed("One Country Membership [First Month Free]")))) %>% 
  mutate(alt_entry = if_else(condition = customer_email_lower %in% c(alt_entry_customers$email),
                             true = "Yes",
                             false = "No"),
         customer_entry = case_when(
           customer_email_lower %in% c(alt_entry_customers$email) ~ "alt_entry",
           customer_email_lower %in% c(bonus_entry_leads$email) ~ "bonus_entry",
           TRUE ~ "Other"
         ),
         grp = case_when(
           product_details %in% c(products_classified$product_details[products_classified$grp == "Member"]) ~ "Member",
           product_details %in% c(products_classified$product_details[products_classified$grp == "One-time"]) ~ "One-time",
           TRUE ~ "Other"
         )) %>% #,
  left_join(x = ., y = big_comm_prods_line_classified, by = c("order_id", "customer_email_lower")) %>% 
  mutate(grp = if_else(condition = !is.na(order_classification),
                       true = order_classification,
                       false = grp),
         product_price = if_else(condition = !is.na(product_sub_group),
                                 true = product_sub_group,
                                 false = product_price),
         order_total = if_else(condition = is.na(order_total),
                               true = product_price,
                               false = order_total)) %>% 
  
  ## Testing ##
  # Could add the exclusions of $0 orders HERE
  # filter(product_price > 0)  # HERE - DO MANUAL CHECKS
  
  filter(!(product_price == 0 & order_total == 0)) %>%  # Trying
  
  ## MAY BE THE TRUE SOLUTION ## tt <- platform_data_classified %>% filter(platform_data_classified$product_price == 0 & platform_data_classified$order_total == 0)  

  #############
  
  select(-c(order_classification, product_sub_group)) %>% 
  mutate(sub_grp = case_when(
    grp == "Member" & product_price %in% c(5.00) ~ "$5",
    (grp == "Member" & product_price %in% c(10.00)) | file_source == "Boldv2.csv" ~ "$10",
    grp == "Member" & product_price %in% c(24.99, 25.00, 25.98) ~ "$25",
    grp == "One-time" & product_price %in% c(10.00) ~ "$10",
    grp == "One-time" & product_price %in% c(24.99, 25.00, 25.98) ~ "$25",
    grp == "One-time" & product_price %in% c(49.95, 49.99, 50.00, 50.96) ~ "$50",
    grp == "One-time" & product_price %in% c(99.95, 99.96, 100.00, 100.99) ~ "$100",
    grp == "alt_entry" & product_price %in% c(5.00) ~ "$5",
    grp == "alt_entry" & product_price %in% c(10.00) ~ "$10",
    grp == "alt_entry" & product_price %in% c(12.00, 12.99) ~ "$12",
    grp == "alt_entry" & product_price %in% c(15.00, 15.99) ~ "$15",
    TRUE ~ "Other"
  ),
  sales_status = if_else(condition = product_details %in% c(products_classified$product_details[products_classified$classification == "Product"]),
                         true = "Product",
                         false = "Other"))

## PERHAPS JOIN TO THE BC ITEMS TO OVERRIDE THOSE CLASSIFICATIONS HERE? ##

# What needs happen?
  # exclude all orders from platform_data_classified that are products only DONE - need to exclude include only one-time and memberships - do it in separate_bc_orders
  # join to the classification for these then replace the value that is currently there DONE
  # Figure out a way to deal with the sub group - already classified above, DONE
    # so this join may have to go above 

#########################################################################

```

## Classify All Purchases According to Customer First Transaction

Notes:
* Identified the first purchase for each customer and classified all subsequent orders to that cohort.
* Identified when the customer is "lost" - If they had a cancellation date, and no orders beyond that cancellation date, considered them lost. 

Additional Context:


```{r}

platform_data_cohorts <- platform_data_classified %>%
# yy <- platform_data_classified %>%   # For testing
  # Don't think I need this part anymore - leave in as reference in case file source is ever relevant again
  # filter(file_source %in% c("BigcommerceOrders.csv" , "GiveOrders.csv" , "ShopifyOrders.csv")) %>%
  
  # For testing individual emails
  
  # filter(customer_email_lower %in% c(
  #   "a.e.flynn@hotmail.com",
  #   "aaronj.garnica@gmail.com"
  #   )) %>% 
  
arrange(customer_email_lower, order_date) %>% 
  group_by(customer_email_lower) %>% 
  mutate(customer_transaction_number_classify = if_else(condition = grp %in% c("Member", "One-time"), 
                                                        true = row_number(),
                                                        false = as.integer(0)),
         customer_transaction_number_classify = na_if(customer_transaction_number_classify, 0),
         customer_transaction_number = row_number(),
         customer_sub_group_transaction_number_classify = if_else(condition = grp == "Member",
                                                                  true = row_number(),
                                                                  false = as.integer(0)),
         customer_sub_group_transaction_number_classify = na_if(customer_sub_group_transaction_number_classify, 0),
         min_customer_sub_group_transaction_number_classify = min(customer_sub_group_transaction_number_classify, na.rm = T),
         first_customer_order = min(customer_transaction_number_classify, na.rm = T),
         min_transaction_date = min(order_date, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(first_order_date = if_else(condition = customer_transaction_number_classify == first_customer_order,
                                    true = order_date,
                                    false = ymd("2099-1-1")),
         first_order_date = na_if(first_order_date, ymd("2099-1-1")),
         cohort_grp = if_else(condition = customer_transaction_number_classify == first_customer_order,
                              true = grp,
                              false = ""),
         cohort_grp = na_if(cohort_grp, ""),
         cohort_sub_grp = if_else(condition = customer_transaction_number_classify == first_customer_order,
                                  true = sub_grp,
                                  false = ""),
         cohort_sub_grp = na_if(cohort_sub_grp, "")) %>% 
  group_by(customer_email_lower, order_date) %>%
  mutate(cohort_grp = if_else(condition = order_date == min_transaction_date & any(grp == "Member"),
                              true = "Member",
                              false = cohort_grp),
         cohort_sub_grp = if_else(condition = any(grp == "Member") &
                                    customer_sub_group_transaction_number_classify == min_customer_sub_group_transaction_number_classify &
                                    !is.infinite(min_customer_sub_group_transaction_number_classify)
                                  & order_date == min_transaction_date,
                                  true = sub_grp,
                                  false = cohort_sub_grp)) %>%
  ungroup() %>%
group_by(customer_email_lower) %>%   
  fill(first_order_date, .direction = "down") %>% 
  fill(cohort_grp, .direction = "down") %>% 
  fill(cohort_sub_grp, .direction = "down") %>% 
  fill(first_order_date, .direction = "up") %>% 
  fill(cohort_grp, .direction = "up") %>% 
  fill(cohort_sub_grp, .direction = "up") %>% 
  ungroup() %>% 
  mutate(cohort = if_else(condition = customer_transaction_number_classify == first_customer_order, 
                          true = paste0(cohort_grp, " ", month(order_date, label = T), "/", year(order_date)),
                          false = ""),
         cohort = na_if(cohort, "")) %>% 
  group_by(customer_email_lower) %>% 
  fill(cohort, .direction = "down") %>% 
  fill(cohort, .direction = "up") %>% 
  mutate(total_transactions = max(customer_transaction_number),
         max_transaction_date = max(order_date, na.rm = T),
         yr_mo_first_order = ymd(paste(year(first_order_date), month(first_order_date), "1", sep = "-"))) %>% 
  fill(max_transaction_date, .direction = "down") %>% 
  ungroup() %>% 
  mutate(transaction_within_past_60_days = if_else(condition = max_transaction_date > (Sys.Date() - 60),
                                                   true = "Yes",
                                                   false = "No"),
         customer_lost = if_else(condition = 
                                   # Leaving in for reference in case cancelation dates from sub platforms come up again
                                   # (!is.na(max_cancel_date) & customer_transaction_number == total_transactions & order_date < max_cancel_date) |
                                   # (!is.na(max_cancel_date) & 
                                      customer_transaction_number == total_transactions & transaction_within_past_60_days == "No"
                                 # )
                                 ,
                                 true = "Lost",
                                 false = "Retained")) %>% 
  rowwise() %>% 
  mutate(months_since_first_purchase = interval(first_order_date, order_date) %/% months(1)) %>% 
  ungroup() %>% 
  filter(months_since_first_purchase >= 0) %>% 
  filter(!(cohort_grp == "Member" & str_detect(string = cohort, pattern = "One-time")))

write_csv(platform_data_cohorts,
          path = "Output Data\\cohorts_classified.csv")

```



```{r}

# Use if not writing data at the time of transformation

# write_csv(platform_data_cohorts,
#           path = "Output Data\\cohorts_classified.csv")

```











